Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-09-17 journal-draft/ettdoc.tex
modify the simulation section

The average number of CCs of the non-singleton clusters is shown in Figure~\ref{ccc_large_scale}.
SOC achieves the most CCs per non-singleton cluster, but the lead over the variants of ROSS decreases significantly when $N$ increases.
%\ie when $N=300$, the number of CCs achieved by ROSS variants (except for ROSS-$\delta$-DFA) is almost the same as that resulted from SOC.
%This means SOC out performs in terms of the average number of CCs per non-singleton cluster when network is sparse.
%This is also observed in the evaluation in Section \ref{ccc_20} where $N=20$.
%When the network becomes denser, even this metric favours SOC as discussed in the beginning of Section~\ref{performance}, ROSS-DGA achieves even more CCs than SOC, and ROSS-DFA and ROSS-$\delta$-DGA increase the number of CCs visibly.

@@

Figure~\ref{false_negative_ccc} shows the average number of CCs decrease slightly when the false negative rate increases.
The size distribution of the ROSS-DGA, ROSS-$\delta$-DGA and SOC is shown in Figure~\ref{false_negative_ccc}.
\begin{figure}[!h]
  \centering
   \includegraphics[width=0.7\linewidth]{false_negative.pdf}
  \caption{The number of CCs per non-singleton cluster with the presence of spectrum sensing false negative}
  %, there are $x=6$ when $N=100$, $x=12$ when $N=200$, $x=21$ when $N=300$, which is around $2/3$ of the number of average neighbours.
  \label{false_negative_ccc}
\end{figure}
%The influence of the false negative on the sustainability of the clusters can be seen from Figure~\ref{false_negative_CDF}.
For all the schemes, when false negative increases, the number of singleton clusters increases accordingly.
%As to the ROSS variants, the changes of the CDF curves are resulted from the increasing singleton clusters.
The clusters from SOC are affected by the sensing errors greatly, \ie when false negative rate is 30\%, a lot more small clusters are generated than that when other false negative rates present.
SOC demonstrates obvious divergence when certain rate of false negative exists, in contrary, ROSS variants are resilient to the false negative in terms of cluster sizes.
The negotiation within the neighborhoods adopted by ROSS variants rules out the channel which is due to false negative successfully, which doesn't work well in SOC.

\begin{figure}[!h]
  \centering
   \includegraphics[width=0.7\linewidth]{draw_cdf_clusterSize_with_false_negative.pdf}
  \caption{100 CRs with false negative in spectrum sensing, 30 PUs in network}
  \label{false_negative_CDF}
\end{figure}

>>>>

The average number of CCs of the non-singleton clusters is shown in Figure~\ref{ccc_large_scale}.
Here we don't see the obvious difference between different schemes on the number of CCs.
%SOC achieves the most CCs per non-singleton cluster, but the lead over the variants of ROSS decreases significantly when $N$ increases.
%This means SOC out performs in terms of the average number of CCs per non-singleton cluster when network is sparse.
%This is also observed in the evaluation in Section \ref{ccc_20} where $N=20$.
%When the network becomes denser, even this metric favours SOC as discussed in the beginning of Section~\ref{performance}, ROSS-DGA achieves even more CCs than SOC, and ROSS-DFA and ROSS-$\delta$-DGA increase the number of CCs visibly.

@@

Figure~\ref{false_negative_ccc} shows the average number of CCs decrease slightly when the false negative rate increases.
The size distribution of the ROSS-DGA, ROSS-$\delta$-DGA and SOC is shown in Figure~\ref{false_negative_CDF}.
\begin{figure}[!h]
  \centering
   \includegraphics[width=0.7\linewidth]{false_negative.pdf}
  \caption{The number of CCs per non-singleton cluster with the presence of spectrum sensing false negative}
  %, there are $x=6$ when $N=100$, $x=12$ when $N=200$, $x=21$ when $N=300$, which is around $2/3$ of the number of average neighbours.
  \label{false_negative_ccc}
\end{figure}
%The influence of the false negative on the sustainability of the clusters can be seen from Figure~\ref{false_negative_CDF}.
For all the schemes, when false negative increases, the number of singleton clusters increases accordingly.
%As to the ROSS variants, the changes of the CDF curves are resulted from the increasing singleton clusters.
The clusters from SOC are affected by the sensing errors the greatly.
More unclustered nodes are generated, and a lot of small clusters are formed, \eg when false negative rate is 30\%.
In contrary, ROSS variants are resilient in terms of unclusterd nodes and cluster sizes.
We can conclude that through negotiation within the neighborhoods, ROSS variants successfully rules out the channel from false negative sensing.
\begin{figure}[!h]
  \centering
   \includegraphics[width=0.7\linewidth]{draw_cdf_clusterSize_with_false_negative.pdf}
  \caption{100 CRs with false negative in spectrum sensing, 30 PUs in network}
  \label{false_negative_CDF}
\end{figure}
